Robust Adaptation to Multi-Scale Climate Variability

### 2019-01-08 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
clean up conclusions and acknowledgements

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{M-N-Sketch.pdf}
  \caption{
    The importance of predicting different signals, and the identifiability and predictability of the signals, depends on the degree of informational uncertainty ($N$) and the project planning period ($M$).
  }\label{fig:m-n-sketch}
\end{figure}
We also showed that the importance of predicting, and potential for doing so skillfully, depend on the project planning period $M$ and the information available, $N$.
\Cref{fig:m-n-sketch} shows that when $M$ and $N$ are short, only a ``rough guess'' using simple models is feasible, and more complex models  only add uncertainty.
As $N$ increases, however, the potential for skillful prediction of \gls{lfv} over the short planning period increases, thereby reducing the cost of a flexible or adaptive instrument.
If $M$ is large, \ie a permanent plan is considered, then informational uncertainty may be addressed with sufficient information (large $N$), but large intrinsic uncertainty may remain.
Finally, if $M$ is long but $N$ is short, then the analysis will lead to the ``danger zone'' of extrapolation and a high potential for misleading estimates.

@@

The authors thank Nandini Ramesh of Columbia University for providing the synthetic NINO3 index from a \SI{100000}{year} run of the Cane-Zebiak model as described in \citet{Ramesh:2016hf}.
The authors thank John High of the United States Army Corps of Engineers for providing the naturalized daily streamflows at the Folsom Dam.
JDG thanks the NSF GRFP program for support (grant DGE 16-44869: ``Understanding \& Predicting Climate Drivers of Extreme, Mid-latitude River Floods'').
DJF thanks SERDP program for support (grant 2516: ``Climate Informed Estimation of Hydrologic Extremes for Robust Adaptation to Non-Stationary Climate'').

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{M-N-Sketch.pdf}
  \caption{
    The importance of predicting different signals, and the identifiability and predictability of the signals, depends on the degree of informational uncertainty ($N$) and the project planning period ($M$).
  }\label{fig:m-n-sketch}
\end{figure}
We also showed that the importance of predicting different climate signals, and potential for doing so skillfully, depend on the project planning period $M$ and the information available, $N$.
\Cref{fig:m-n-sketch} shows that when $M$ and $N$ are short, only a ``rough guess'' using simple models is feasible, and more complex models  only add uncertainty.
As $N$ increases, however, the potential for skillful prediction of \gls{lfv} over the short planning period increases, thereby reducing the cost of a flexible or adaptive instrument.
If $M$ is large, \ie a permanent plan is considered, then informational uncertainty may be addressed with sufficient information (large $N$), but large intrinsic uncertainty may remain.
Finally, if $M$ is long but $N$ is short, then the analysis will lead to the ``danger zone'' of extrapolation and a high potential for misleading estimates.

@@

The authors thank Nandini Ramesh of Columbia University for providing the synthetic NINO3 index from a \SI{100000}{year} run of the Cane-Zebiak model as described in \citet{Ramesh:2016hf}.
The authors thank John High of the United States Army Corps of Engineers for providing the naturalized daily streamflows at the Folsom Dam.
JDG thanks the NSF GRFP program (grant DGE 16-44869: ``Understanding \& Predicting Climate Drivers of Extreme, Mid-latitude River Floods'') and SERDP program (grant 2516: ``Climate Informed Estimation of Hydrologic Extremes for Robust Adaptation to Non-Stationary Climate'') for support.
